SeedLing: Building and using a seed corpus \\ for the Human Language Project

### 2014-04-28 docs/computEL-final/clean.tex
New new heatmap

>>>>

For some languages, there is more than one standard orthography. For example, Mandarin Chinese is written with either traditional and simplified characters; Serbian is written with either the Cyrillic or the Roman alphabet. For cross-linguistic NLP, it would be helpful to have codes for orthographies, but unfortunately no standards exist for this purpose.
